Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-26 WRITEUP/ms.tex
polish sec 7

We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of 
molecule gas structures. The high virial parameter found for some MCCs in \flower 
indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, 
where energy quickly dissipates. % with low virial parameters.
This is consistent with the notion that collapsing structures resulting from
gravitational instability occur within globally stable structures, which are
supported by turbulence and rotation on large scale.
%% 
%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales. 
%Low-$Q$ sets the regions that fragments 
%and within those regions where alphavir is low enough is where structures to further collapse to form stars. 
This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
and thus, \SF in the first galaxies.

% end
Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
While observations leveraging the combination of spatial-spectral imaging of
multi-band continuum and spectral line emission are crucial, 
we shown in this work that prototypical galaxies at the EoR with properties similar to \flower
are expected to have molecular gas structures on sub-kpc scales; however, these are not 
the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from 
large-scale motions even in the dispersion dominated stage. 
This results means that caution should be taken when interpreting observational data, albeit the impressive resolution and sensitivity that are unprecedented. 
Careful consideration of large-scale motions is required when interpreting the observed data in order to understand the origin of star formation activity 
in galaxies at EoR. 
It is thus currently unclear whether \highz molecular gas structures are intrinsically more turbulent than those in the local ISM. 
This will become clearer in the next few years as deep and high resolution imaging of molecular gas at \highz are obtained with ALMA and NOEMA.

On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining 
and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
These predictions can in turn be 
tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
enabling us to test our findings and refine future simulations to shed light on the physical processes behind
\SF since the cosmic dark ages.

>>>>

We perform virial analysis, as motivated by \obs, where the virial parameter is used as a surrogate to comparing the potential to kinetic energies of 
molecule gas structures. The high virial parameter found for some MCCs in \flower 
indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$.
On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are unstable
and \SF is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, 
where energy quickly dissipates. % with low virial parameters.
This is consistent with the notion that collapsing structures result from
gravitational instability occuring within globally stable structures, which are
supported by turbulence and rotation on large scale.
%% 
%Our results suggest that the more massive and bigger MCCs compared to the Milky Way
%manifest from the higher gas mass fraction, surface density, and velocity dispersion, but \SF takes place on much smaller scales. 
%Low-$Q$ sets the regions that fragments 
%and within those regions where alphavir is low enough is where structures to further collapse to form stars. 
This also implies \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores),
and thus, \SF in the first galaxies.

% end
Determining the multi-phase ISM properties of early galaxies
is a critical piece to understanding the evolution and
assembly history of galaxies, since they set the pace
for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
While observations leveraging the combination of spatial-spectral imaging of
multi-band continuum and spectral line emission are crucial, 
we show in this work that prototypical galaxies at the EoR with properties similar to \flower
are expected to have molecular gas structures on sub-kpc scales; however, these are not 
the truly star-forming regions. The linewidth of molecular gas structures probed on these scales partially results from 
large-scale motions even in a highly disturbed stage.
This means that caution should be taken when interpreting observational data, 
albeit the impressive resolution and sensitivity that are unprecedented. 
%Careful consideration of large-scale motions is required 
%when interpreting the observed data in order to understand the origin of star formation activity in galaxies at EoR. 
It is thus currently unclear whether \highz molecular gas structures are truly intrinsically more turbulent than those in the local ISM. 
This will become clearer in the next few years as deeper and higher resolution imaging of 
molecular gas at \highz are observed with ALMA and NOrthern Extended Millimeter Array (NOEMA). 
On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy
statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining 
and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
%These predictions can in turn be 
%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
%\SF since the cosmic dark ages.
